\Large{Adversarial Training against Systematic Uncertainty}

### 2016-09-29 tex/paper.tex
save

Systematic uncertainties in high energy physics, representing our incomplete
knowledge in the simulation of physical processes or in the detection apparatus,
may cause variations in the conditional distributions of features used for
training a classifier.  As such, the efficacy of a classifier may change under
the variations caused by systematic uncertainties.  In this paper, we repurpose
adversarial training as a means to produce a pivotal classifier which is
invariant to variations of the nuisance parameters describing the
effects of systematic uncertainties. In the machine learning context, this
problem is closely related to those of domain adaptation and enforcing fairness
in classification. Following that line of work, the method proposed in this work
can be regarded as generalization that also supports the continuous case,
which can be viewed as handling infinitely many domains or as enforcing fairness
over continuous attributes.

@@

\item Uncertainties on the detection apparatus and its effect on the
  measurement of particle properties, giving rise to uncertainties on
  the distributions $p(X|Y)$.  For instance, this includes
  uncertainties on our knowledge of the mean and variance of the
  measured energy distribution of a particle.
\end{itemize}
In this paper, we will not address uncertainties of the first type
mentioned above (uncertainties on the priors).  Rather, we will focus
on mitigating the effect of systematic uncertainties that alter the
conditional distributions $p(X|Y)$.

>>>>

Systematic uncertainties in high energy physics represent our incomplete
knowledge in the simulation of physical processes or in the properties of the
detection apparatus. In effect, systematic uncertainties may cause variations in
the conditional distributions of the features used for training a predictive
model like a classifier, thereby altering its decisions and resulting efficacy.
In this paper, we repurpose adversarial training as a means to produce a pivotal
classifier which is invariant to variations of the nuisance parameters
describing the effects of systematic uncertainties. In the machine learning
context, this problem is closely related to those of domain adaptation and
enforcing fairness in classification. Following that line of work, the proposed
method can be regarded as generalization that also supports the continuous case,
which can be viewed as handling infinitely many domains or as enforcing fairness
over continuous features.

@@

\item Uncertainties on the detection apparatus and its effect on the
  measurement of particle properties, giving rise to uncertainties on
  the distributions $p(X|Y)$.  For instance, this includes
  uncertainties on our knowledge of the mean and variance of the
  measured energy distribution of a particle.
\end{itemize}
In this paper, we will not address uncertainties of the first type
mentioned above (uncertainties on the priors).  Rather, we will focus
on mitigating the effect of systematic uncertainties that alter the
conditional distributions $p(X|Y)$. \glnote{Remove this comment?}
